---
title: "Assignment 1"
author: "Group 8"
date: "2024-02-11"
output:
  html_document:
    df_print: paged
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

We are hired as a Data Analyst to perform an analysis based on historical data. The key objective is to perform data analysis using R Programming.

This is the data set

``` {r}
Life.Expectancy.Data <- read.csv("C:/Users/Turjo/OneDrive/Desktop/TRINA STUDY/Third Semester/4066 Analytics/Life Expectancy Data.csv")
```

Q1. Print the structure of your dataset

``` {r}
str(Life.Expectancy.Data)
```

Q2. List the variables in your dataset

``` {r}
names(Life.Expectancy.Data)
```

Q3. Print the top 15 rows of your dataset

``` {r}
head(Life.Expectancy.Data, n = 15)
```


Q4. Write a user defined function using any of the variables from the data set.

``` {r}
cube_alcohol = function(alcohol){alcohol^3}
cube_alcohol(Life.Expectancy.Data$Alcohol)

```


Q5. Use data manipulation techniques and filter rows based on any logical criteria that exist in your dataset.

``` {r}
library(tidyverse)
countryBD = as.data.frame(Life.Expectancy.Data %>% filter(Life.Expectancy.Data$Country == "Bangladesh"))
view(countryBD)

```


Q6. Identify the dependent & independent variables and use reshaping techniques and create a new data frame by joining those variables from your dataset.

``` {r}
Newtable1 = cbind(Life.Expectancy.Data$Country, Life.Expectancy.Data$Status, Life.Expectancy.Data$Life.expectancy)
view(Newtable1)
Newtable3 = cbind(Life.Expectancy.Data$Country, Life.Expectancy.Data$infant.deaths, Life.Expectancy.Data$GDP, Life.Expectancy.Data$Population)
view(Newtable3)
Totaltable = merge(Newtable1, Newtable3, by = "V1")
view(Totaltable)
```



Q7. Remove missing values in your dataset.


``` {r}
Life.Expectancy.Data = as.data.frame(na.omit(Life.Expectancy.Data))
```


Q8. Identify and remove duplicated data in your dataset


``` {r}
lifex = as.data.frame(Life.Expectancy.Data %>% distinct(GDP, .keep_all = TRUE) )
```


Q9. Reorder multiple rows in descending order

``` {r}
lifex2 = as.data.frame(Life.Expectancy.Data %>% arrange( desc(Year)))
```

Q10. Rename some of the column names in your dataset

``` {r}
names(Life.Expectancy.Data)[4]= "Life Expectency"
names(Life.Expectancy.Data)[5] = "Adult Mortality"
names(Life.Expectancy.Data)[6] = "Infant Deaths"

```

Q11. Add new variables in your data frame by using a mathematical function (for e.g. – multiply an existing column by 2 and add it as a new variable to your data frame)


``` {r}
Life.Expectancy.Data = as.data.frame(Life.Expectancy.Data %>% mutate( Double.Schooling = Life.Expectancy.Data$Schooling * 2))

```


Q12. Create a training set using random number generator engine.

``` {r}
lifex3 = cbind(Life.Expectancy.Data$Country, Life.Expectancy.Data$Year, Life.Expectancy.Data$Status, Life.Expectancy.Data$`Life Expectency`, Life.Expectancy.Data$`Adult Mortality`)
lifex3 = as.data.frame(lifex3)
set.seed(1234)
lifex3 = as.data.frame(lifex3 %>% sample_frac(0.8, replace = FALSE) )
view(lifex3)

```



Q13. Print the summary statistics of your dataset


``` {r}
summary(Life.Expectancy.Data)

```


Q14. Use any of the numerical variables from the dataset and perform the following statistical functions

Mean

``` {r}
mean(Life.Expectancy.Data$`Life Expectency`)

```


Median

``` {r}
median(Life.Expectancy.Data$`Life Expectency`)
```


Mode


``` {r}
mode(Life.Expectancy.Data$`Life Expectency`)
```


Range

``` {r}
range(Life.Expectancy.Data$`Life Expectency`)
```


Q15. Plot a scatter plot for any 2 variables in your dataset

``` {r}
ggplot(data = Life.Expectancy.Data, aes( x = Life.Expectancy.Data$`Life Expectency`, y = Life.Expectancy.Data$`Infant Deaths`)) + geom_point()
```


Q16. Plot a bar plot for any 2 variables in your dataset

``` {r}
ggplot(Life.Expectancy.Data, aes(x = Life.Expectancy.Data$`Life Expectency`))+ geom_bar(fill = "darkorchid4")
```


Q17. Find the correlation between any 2 variables by applying least square linear regression mode

``` {r}
lifeexCorr = cor(Life.Expectancy.Data$percentage.expenditure, Life.Expectancy.Data$GDP, method = "pearson")
lifeexCorr

```

```{r pressure, echo=FALSE}

```
